---
output: rmarkdown::github_document
---

# ipinfo

Collect Metadata on 'IP' Addresses and Autonomous Systems

## Description

The 'ipinfo.io' <https://ipinfo.io/> service provides an 'API' for retrieving metadata on 'IP' addresses and autonomous systems. Methods are provided to query and retrieve this metadata.
   
## What's Inside The Tin

The following functions are implemented:

- `country_trans`:	Retrieve a data frame of country abbreviation to name mappings
- `query_asn`:	Retrieve full ASN details
- `query_ip`:	Retrieve full IP details

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/ipinfo")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
library(dplyr)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(ipinfo)

# current verison
packageVersion("ipinfo")
```

### Lookup an IP

```{r cache=TRUE}
str(
  query_ip("1.1.1.1"),
  1
)
```

### Lookup an ASN

I do not have a paid plan for this so I cannot test it

### Country iso2c to name mapping

```{r cache=TRUE}
country_trans()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.